This is an example of article title

### 2021-10-07 paper/header.tex

\title{CompositionalNetworks.jl: a scaling glass-box neural network for combinatorial functions learning}

\author[1]{Jean-François \textsc{Baffier}}
\author[2]{Khalil \textsc{Chrit}}
\author[34]{Florian \textsc{Richoux}}
\author[2]{Pedro \textsc{Patinho}}
\author[2]{Salvador \textsc{Abreu}}
\affil[1]{IIJ Innovation Institute, Japan}
\affil[2]{NOVA-LINCS, University of Évora, Portugal}
\affil[3]{AIST, Japan}
\affil[4]{JFLI, CNRS, Japan}

\keywords{Julia, Optimization, Constraint Programming, Neural Network, Scaling Learning}

\hypersetup{
pdftitle = {CompositionalNetworks.jl: a scaling glass-box neural network for combinatorial functions learning},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Jean-François \textsc{Baffier}, Khalil \textsc{Chrit}, Florian \textsc{Richoux}, Pedro \textsc{Patinho}, Salvador \textsc{Abreu}},
pdfkeywords = {Julia, Optimization, Constraint Programming, Neural Network, Scaling Learning},
}

>>>>

\title{CompositionalNetworks.jl: a scaling glass-box neural network to learn combinatorial functions}

\author[1]{Jean-François \textsc{Baffier}}
\author[2]{Khalil \textsc{Chrit}}
\author[34]{Florian \textsc{Richoux}}
\author[2]{Pedro \textsc{Patinho}}
\author[2]{Salvador \textsc{Abreu}}
\affil[1]{IIJ, Japan}
\affil[2]{NOVA-LINCS, University of Évora, Portugal}
\affil[3]{AIST, Japan}
\affil[4]{JFLI, CNRS, Japan}

\keywords{Julia Language, Constraint Programming, Local Search, Metaheuristics, Neural Network, Metaprogramming, Scalable Machine Learning, Glass-Box Algorithm}

\hypersetup{
pdftitle = {CompositionalNetworks.jl: a scaling glass-box neural network to learn combinatorial functions},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Jean-François \textsc{Baffier}, Khalil \textsc{Chrit}, Florian \textsc{Richoux}, Pedro \textsc{Patinho}, Salvador \textsc{Abreu}},
pdfkeywords = {Julia Language, Constraint Programming, Local Search, Metaheuristics, Neural Network, Metaprogramming, Scalable Machine Learning, Glass-Box Algorithm},
}

### 2021-10-07 paper/paper.tex

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}

@@

\newcommand{\jc}{\href{https://github.com/JuliaConstraints}{JuliaConstraints}\xspace}
\newcommand{\cdjl}{\href{https://github.com/JuliaConstraints/ConstraintDomains.jl}{ConstraintDomains.jl}\xspace}
\newcommand{\cnjl}{\href{https://github.com/JuliaConstraints/CompositionalNetworks.jl}{CompositionalNetworks.jl}\xspace}
\newcommand{\cjl}{\href{https://github.com/JuliaConstraints/Constraints.jl}{Constraints.jl}\xspace}
\newcommand{\cmjl}{\href{https://github.com/JuliaConstraints/ConstraintModels.jl}{ConstraintModels.jl}\xspace}
\newcommand{\lssjl}{\href{https://github.com/JuliaConstraints/LocalSearchSolvers.jl}{LocalSearchSolvers.jl}\xspace}
\newcommand{\cblsjl}{\href{https://github.com/JuliaConstraints/CBLS.jl}{CBLS.jl}\xspace}

@@

\begin{abstract}
  Interpretable Compositional Networks (ICNs) are a neural network variant for combinatorial function learning that allows the user to obtain interpretable results, unlike ordinary artificial neural networks. An ICN outputs a composition of functions that scale with the size of the input, allowing a learning phase on relatively small spaces.
  \cnjl is a pure Julia package that exploits the language's meta-programming, parallelism and multiple dispatch features to produce learned compositions in mathematical and programming languages such as Julia, C or C++.
\end{abstract}

@@

\begin{figure}[t]
  \centering
  \subcaptionbox{CSP landscape\label{sfig:csp}}{
    \includegraphics[width = .95\columnwidth]{figs/csp_landscape_complex_zero_big.png}
  }

  \subcaptionbox{EFSP landscape\label{sfig:efsp}}{
    \includegraphics[width = .95\columnwidth]{figs/efsp_landscape_complex_zero_big.png}
  }\caption{
    Comparison of a Constraint Satisfaction Problem (CSP) and an Error
    Function Satisfaction Problem (\efsp) landscapes. The finer scale
    in the error heuristic of the \efsp leads to a better convergence
    rate.}\label{fig:landscape}
\end{figure}

@@

\subsection{A first C++ library}
\label{subsec:cplusplus}

@@

As mentioned in Section \ref{sec:xlc}, \cnjl generates code for a direct use in Julia, but also exports usable code for both the GHOST(C++) and AdaptiveSearch (C)\footnote{This feature is a WIP at the moment this article is submitted, but is expected to be completed in the coming weeks.}. The code exported in C++, that is the \emph{operations} of each neuron, is strongly inspired by our C++ library.

@@

The \cnjl package is part of the \jc GitHub organization that proposes a first collection of Julia packages for Constraint-Based Local Search (CBLS), a subfield of Constraint Programming.

@@

The LocalSearchSolvers.jl package is a Constraint-Based Local Search framework started in Fall 2020 and inspired by other CBLS solvers such as GHOST (C++) and AdaptiveSearch (C) that allows users to tune their own solver.

During the development of LocalSearchSolvers.jl, we decided to split the code and functionality of the original framework into several independent packages for ease of maintenance and in hopes of providing common tools for other constraint programming packages in Julia.

During 2021, these tools were collected into the \jc ecosystem as follows
\begin{itemize}
  \item \cdjl: creation of discrete, continuous, and arbitrary domain (beta status)
  \item \cjl: generation of constraints from a boolean concept or an error function. Also list usual constraints and their properties (beta status)
  \item \cnjl: stable
  \item \lssjl: A CBLS framework in Julia with built-in parallel and distributed scalability
  \item \cblsjl: A MOI/JuMP wrapper for LocalSearchSolvers
  \item \cmjl: list of CP models for \cblsjl and \lssjl
\end{itemize}

The global state of the Constraint Programming ecosystem is presented in Figure \ref{fig:overview}. Beside the CBLS framework of \jc, other solvers are complete search methods, such as ConstraintSolver.jl\footnote{\url{https://github.com/Wikunia/ConstraintSolver.jl}}, CPLEXCP.jl\footnote{\url{https://github.com/dourouc05/CPLEXCP.jl}}, and SeaPearl.jl \cite{chalumeau2021seapearl}.

@@

@@

\begin{figure}[t]
  \centerline{\includegraphics[page=1]{figs/magicsquare.pdf}}
  \caption{A solved magic-square of size $3$. The \emph{magic sum} is equal to $15$. Image from Wikipedia's user \textsc{Phidauex}.}
  \label{fig:magicsquare}
\end{figure}

In \texttt{ConstraintModels.jl}, we use the following code to generate a magic-square instance.

@@

function magic_square(n::Integer)
model = Model(CBLS.Optimizer)
N = n^2
Σ = n * (N + 1) / 2
@variable(model, 1 <= X[1:n, 1:n] <= N, Int)
@constraint(model, vec(X) in AllDifferent())
for i in 1:n
  @constraint(model, X[i,:] in Linear(Σ))
  @constraint(model, X[:,i] in Linear(Σ))
end
@constraint(model,
  [X[i,i] for i in 1:n] in Linear(Σ)
)
@constraint(model,
  [X[i,n+1-i] for i in 1:n] in Linear(Σ)
)
  return model, X
end

# Create a magic square instance of size 4x4
m, X = magic_square(4)
# Optimize
optimize!(m)
# Output values
@info values.(X)
\end{lstlisting}

@@

\cnjl extends the work of the first C++ library used in \cite{richoux2020automatic}. As mentioned in Section \ref{subsec:cplusplus}, that library used for prototyping was limited through several aspects: this, this, and that. Obviously, those limitations could have been lifted in the first library. However, we decided to use some features of the Julia language to ease provisioning flexibility and broader features to ICNs.

\paragraph*{Block about Julia} test

@@

A layer is defined by a non-empty collection of (possibly mutually exclusive) operations. The original ICN is composed of four layers: \emph{transformation} (exclusive), \emph{arithmetic}, \emph{aggregation}, and \emph{comparison}.

@@

@@

@@

All methods required for the definition of additional layers are all available.

@@

We store the composition of an ICN in three forms:
\begin{itemize}
  \item A collection of \texttt{Symbol}s per layer of the ICN that allows the generation of code as a string
  \item The Julia object of type \texttt{Function} to apply the composition directly
\end{itemize}

@@

The result output by an ICN is a composition, a mathematical function composed of several basic operations. The \texttt{code} function returns the definition of a composition in either a mathematical or programming language. From \emph{v1.0} of \cnjl, \texttt{code} accepts \texttt{:maths, :Julia, :C, :Cpp} as values for the \emph{lang} key argument.

@@

\section{Explore, learn, and compose}
\label{sec:xlc}

It is far from practical to apply the internals of \cnjl step-by-step. We provide a user-friendly sequence of higher-level actions, \emph{explore}, \emph{learn}, and \emph{compose} that fits most of expected uses of this package.

Each of those actions is semi-automated through default parameters and machine learning over a large collection of benchmarks \cite{baffier2022interpretable}.

\subsection{Exploration}

\begin{lstlisting}[language = Julia]
function explore(
  domains,
  concept,
  param=nothing;
  search=:flexible,
  complete_search_limit=10^6,
  max_samplings=sum(domain_size, domains),
  solutions_limit=floor(Int, sqrt(max_samplings)),
)
  if search == :flexible
    search = sum(domain_size, domains) <
      complete_search_limit ? :complete : :partial
  end
  return explore(Val(search), domains, concept,
    param, solutions_limit, max_samplings
  )
end
\end{lstlisting}

@@

\begin{itemize}
  \item Add new operations in existing layers
  \item Add new layers
  \item Use reinforcement learning
  \item Cover more metrics
  \item Apply ICN to other field than EFN for CBLS solvers
\end{itemize}

@@

The problems modelled, and the compositions extracted in this section are subject to future changes and improvements of the JuMP/JuCP packages. However, the keys ideas are presented here and examples will be updated accordingly within \jc in the future.

@@

@@

@@

  @constraint(m, X in AllDifferent())
  @constraint(m, X in Ordered()) # optional

@@

Along with the magic-square model in Section \ref{sec:introduction}, the models in this zoo use the following constraints: \texttt{:all\_different}, \texttt{:dist\_different}, \texttt{:linear}, and \texttt{:ordered}.

>>>>

\usepackage[section]{placeins}

% \usepackage{float}

\hypersetup{colorlinks=false,linkcolor=blue,urlcolor=blue}

@@

\newcommand{\jc}{\href{https://github.com/JuliaConstraints}{JuliaConstraints}\xspace}
\newcommand{\cdjl}{\href{https://github.com/JuliaConstraints/ConstraintDomains.jl}{ConstraintDomains.jl}\xspace}
\newcommand{\cnjl}{\href{https://github.com/JuliaConstraints/CompositionalNetworks.jl}{CompositionalNetworks.jl}\xspace}
\newcommand{\cjl}{\href{https://github.com/JuliaConstraints/Constraints.jl}{Constraints.jl}\xspace}
\newcommand{\cmjl}{\href{https://github.com/JuliaConstraints/ConstraintModels.jl}{ConstraintModels.jl}\xspace}
\newcommand{\lssjl}{\href{https://github.com/JuliaConstraints/LocalSearchSolvers.jl}{LocalSearchSolvers.jl}\xspace}
\newcommand{\cblsjl}{\href{https://github.com/JuliaConstraints/CBLS.jl}{CBLS.jl}\xspace}
\newcommand{\icnbjl}{\href{https://github.com/JuliaConstraints/ICNBenchmarks.jl}{ICNBenchmarks.jl}\xspace}

@@

\begin{abstract}
  Interpretable Compositional Networks (ICNs) are a neural network variant for combinatorial function learning that allows the user to obtain interpretable results, unlike ordinary artificial neural networks. An ICN outputs a composition of functions that scales with the size of the input, allowing a learning phase on relatively small spaces.
  \cnjl is a pure Julia package that exploits the language's meta-programming, parallelism and multiple dispatch features to produce learned compositions in mathematical and programming languages such as Julia, C or C++.
\end{abstract}

@@

\begin{figure*}[t]
  \centering
  \subcaptionbox{CSP landscape\label{sfig:csp}}{
    \includegraphics[width = .95\columnwidth]{figs/csp_landscape_complex_zero_big.png}
  }
  \hfill
  \subcaptionbox{EFSP landscape\label{sfig:efsp}}{
    \includegraphics[width = .95\columnwidth]{figs/efsp_landscape_complex_zero_big.png}
  }\caption{
    Comparison of a Constraint Satisfaction Problem (CSP) and an Error
    Function Satisfaction Problem (\efsp) landscapes. The finer scale
    in the error heuristic of the \efsp leads to a better convergence
    rate.}\label{fig:landscape}
\end{figure*}

@@

% \subsection{A first C++ library}
% \label{subsec:cplusplus}

@@

As mentioned in Section \ref{sec:use}, \cnjl generates code for a direct use in Julia, but also exports usable code for both the GHOST(C++) and AdaptiveSearch (C)\footnote{This feature is a WIP at the moment this article is submitted, but is expected to be completed in the coming weeks.}. The code exported in C++, that is the \emph{operations} of each neuron, is strongly inspired by our C++ library.

This work is part of a collection of articles that introduce the theoretical background of ICN \cite{richoux2020automatic}, a user-friendly implementation in Julia, and an extensive collection of benchmarks \cite{baffier2022interpretable}.
Please note that the default parameters, and semi-automated learning parameters for advanced users, in \cnjl will improve along the results in \cite{baffier2022interpretable} computed from \icnbjl on an HPC cluster.

\FloatBarrier

@@

The \cnjl package is part of the \jc GitHub organization that proposes a first collection of Julia packages for Constraint-Based Local Search (CBLS), a subfield of Constraint Programming. All packages fall under the MIT license.

@@

The \lssjl package is a Constraint-Based Local Search framework started in Fall 2020 and inspired by other CBLS solvers such as GHOST (C++) and AdaptiveSearch (C) that allows users to tune their own solver.

During the development of LocalSearchSolvers.jl, we decided to split the code and functionality of the original framework into several independent packages for ease of maintenance and in hopes of providing common tools for other constraint programming packages in Julia. These tools were collected into the \jc ecosystem.

The global state of the Constraint Programming ecosystem is presented in Figure \ref{fig:overview}. Beside the CBLS framework of \jc detailed below, other solvers are complete search methods, such as ConstraintSolver.jl\footnote{\url{https://github.com/Wikunia/ConstraintSolver.jl}}, CPLEXCP.jl\footnote{\url{https://github.com/dourouc05/CPLEXCP.jl}}, and SeaPearl.jl \cite{chalumeau2021seapearl}.

\paragraph*{State of the packages in \jc}

\begin{itemize}
  \item Stable packages
  \begin{itemize}
    \item \cnjl: internal tool to provide semi-automated error functions. Also, a standalone to learn compositions for combinatorial functions\footnote{At the time of submission, \cnjl is not yet release as \texttt{v1}. Some minor changes are expected from the results of the benchmarks in \cite{baffier2022interpretable} that will be submitted at the end of October.}
  \end{itemize}
  \item Beta packages (usable with frequent breaking changes)
  \begin{itemize}
    \item \cdjl: creation of discrete, continuous, and arbitrary domains
    \item \cjl: generation of constraints from a boolean concept or an error function. Also, list usual constraints and their properties
    \item \lssjl: A CBLS framework in Julia with built-in parallel and distributed scalability
    \item \cblsjl: A MOI/JuMP wrapper for LocalSearchSolvers
    \item \cmjl: list of CP models for \cblsjl and \lssjl
  \end{itemize}

\end{itemize}

\subsection{The \emph{JuMP} ecosystem} % 3-6p
\label{subsec:jump}

JuMP is a modeling language accessible through its main package
JuMP.jl \cite{DunningHuchetteLubin2017} and many supporting Julia packages. Beneath JuMP is an
abstraction layer called MathOptInterface
(MOI)~\cite{MathOptInterface-2021}. One can make a parallel
between MOI/JuMP and FlatZinc/MiniZinc~\cite{nethercote2007minizinc},
common modeling tools of the Constraint Programming community.
Recently, the
\href{https://github.com/dourouc05/ConstraintProgrammingExtensions.jl}{ConstraintProgrammingExtensions.jl}
package that extends MOI/JuMP to the Constraint Programming world was
made available. It is likely to become the recommended unified JuMP
modeling extension for the Julia Constraint Programming solvers.

@@

\begin{figure}[t]
  \centerline{\includegraphics[page=1, width=.75\columnwidth]{figs/magicsquare.pdf}}
  \caption{A solved magic-square of size $3$. The \emph{magic sum} is equal to $15$. Image from Wikipedia's user \textsc{Phidauex}.}
  \label{fig:magicsquare}
\end{figure}

Our CBLS framework uses three levels of modeling syntax: a \emph{raw} Julia syntax, and both MOI and JuMP syntaxes. In this article, we will only use the highest level one, the JuMP syntax.

@@

In \cmjl, we use the following code to generate a magic-square instance.

@@

function magic_square(n::Integer)
model = Model(CBLS.Optimizer)
N = n^2
Σ = n * (N + 1) / 2
@variable(model, 1 <= X[1:n, 1:n] <= N, Int)
@constraint(model, vec(X) in AllDifferent())
for i in 1:n
  @constraint(model, X[i,:] in Linear(Σ))
  @constraint(model, X[:,i] in Linear(Σ))
end
@constraint(model,
  [X[i,i] for i in 1:n] in Linear(Σ)
)
@constraint(model,
  [X[i,n+1-i] for i in 1:n] in Linear(Σ)
)
  return model, X
end
\end{lstlisting}

@@

As mentioned in Subsection \ref{subsec:icn}, \cnjl extends the work of the first C++ library used for prototyping in \cite{richoux2020automatic}. We decided to use some features of the Julia language to ease provisioning flexibility and broader features to ICNs.

\subsection{The Julia language}
\label{subsec:julialang}

The Julia language was introduced in~\cite{bezanson2017julia} and
purports to be a new take on \emph{mathematical programming}.  Some
key features of the language, according to the official website, which
led us to consider it as an implementation vehicle:
\begin{description}
\item[Fast:] Julia was designed from the beginning for high
  performance.  Julia programs compile to efficient native code for
  multiple platforms via LLVM~\cite{lattner2004llvm}.
\item[Dynamic:] It is dynamically typed, feels like a scripting
  language, and has good support for interactive use.
\item[Reproducible:] Reproducible environments make it possible to
  recreate the same Julia environment every time, across platforms,
  with pre-built binaries.
\item[Composable:] It uses multiple dispatch as a paradigm, making it
  easy to express many object-oriented and functional programming
  patterns.
\item[General-purpose:] It provides metaprogramming, asynchronous I/O,
  debugging, logging, profiling, a package manager, and more.  One can
  build entire Applications and Microservices in Julia.
\item[Open source:] It is an open source project with over 1,000
  contributors.  It is made available under the MIT license and the
  source code is available on GitHub.
\end{description}

@@

A layer is defined by a non-empty collection of (possibly mutually exclusive) operations. Our basic ICN (for \efsp/\efop) is composed of four layers: \emph{transformation}, \emph{arithmetic} (exclusive), \emph{aggregation} (exclusive), and \emph{comparison} (exclusive). An illustration is given as Figure \ref{fig:model_icn}. The \texttt{Layer} structure stores these operations.

@@

The most complex layer is probably the \emph{transformation} layer. An operation (neuron) of this layer is defined over a vector of values and an optional parameter. As it is often simpler to define a transformation as a function over a specific index of the input vector, we provide meta-programming utility functions to generate vectorized methods: \texttt{lazy} and \texttt{lazy\_param}.

@@

When a concept is provided to an ICN, the user can provide an optional parameter input with the keyword argument \texttt{param}. A layer will be generated with or without the parametric operations (neurons) based on \texttt{param}'s value. Follow a shortened version of the transformation layer generator.

@@

All methods required for the definition of additional layers are all available. An (unweighted) ICN is simply generated from a sequence of layers. After a learning phase using the a genetic algorithm from \texttt{Evolutionary.jl}\footnote{\url{https://github.com/wildart/Evolutionary.jl}}, this ICN can output a composition in various forms.

@@

Once the ICN is weighted, we store its  output as a composition with three forms.
A collection of \texttt{Symbol}s per layer of the ICN that allows the generation of code as a pre-process in any language, assuming the operations encoding in that language are available. \cnjl currently supports Julia, C, and C++.

A composition also stores a Julia object of type \texttt{Function} to apply the composition in a dynamic fashion.

@@

As mentioned above, an ICN outputs a composition, \ie{} a mathematical function composed of several basic operations. The \texttt{code} function returns the definition of a composition in either a mathematical or a programming language. From \texttt{v1} of \cnjl, \texttt{code} accepts \texttt{:maths} (default), \texttt{:Julia}, \texttt{:C}, \texttt{:Cpp} as values for the \texttt{lang} keyword argument.

@@

\section{How to use \cnjl}
\label{sec:use}

This section covers the essential steps to use ICN in a Julia environment. The actions required are few, which allow users to apply or export compositions effortlessly.

\subsection{Installation and import}
\label{subsec:install}

\cnjl will keep compatibility with the latest stable and LTS releases of Julia\footnote{Note that at the time of writing, Julia has just released \texttt{v1.7}. Compatibility with last LTS will start from the next LTS release.}. We recommend the users to install the latest version of Julia\footnote{\url{https://julialang.org/downloads/}} and to call it with \texttt{julia -t auto} which launch Julia with all available threads on the local machine. Installing \cnjl from the Julia REPL is as simple as:

\begin{lstlisting}[language = Julia]
using Pkg
Pkg.update()
Pkg.add("CompositionalNetworks")
\end{lstlisting}

Alternatively, one can install from the package REPL (simply press `]' in a Julia session) in a single command.

\begin{lstlisting}
add CompositionalNetworks
\end{lstlisting}

Finally, loading the package is done by calling:
\begin{lstlisting}[language = Julia]
using CompositionalNetworks
\end{lstlisting}

Note that from Julia \texttt{v1.7}, calling \texttt{using} on uninstalled package will prompt the user to install it. Hence, the last command is the only one strictly required.

\subsection{Explore, learn, and compose}
\label{subsec:xlc}

It is far from practical to apply the internals of \cnjl step-by-step. We provide a user-friendly sequence of higher-level actions that fits most of expected uses of this package:
\begin{itemize}
  \item \emph{explore} a search space according to a collection of variables domains, a metric, and a concept with an optional parameter
  \item \emph{learn} the weights of an ICN on that space according to the same metric
  \item \emph{compose} the elementary operations according to the weights of the ICN
\end{itemize}

The whole sequence can be executed through \texttt{explore\_learn\_compose}. That function accepts an increasingly large collection of (keyword) arguments:
\begin{itemize}
  \item \texttt{domains}: domains of the variables that define the training space
  \item \texttt{concept}: the concept of the targeted constraint
  \item \texttt{param}: an optional parameter of the constraint
  \item \texttt{search}: either \texttt{:flexible},\texttt{:partial} or \texttt{:complete} search. Flexible search will use \texttt{search\_limit} and \texttt{solutions\_limit} to determine if the search space needs to be partially or completely explored
  \item \texttt{global\_iter}: number of learning iterations
  \item \texttt{local\_iter}: number of generations in the underlying genetic algorithm
  \item \texttt{metric}: the metric to measure the distance between a configuration and known solutions
  \item \texttt{pop\_size}: size of the population in the genetic algorithm
  \item \texttt{complete\_search\_limit}: used in conjunction with \texttt{solution\_limit} to determine if a flexible search is set to complete or partial
  \item \texttt{solutions\_limit}: see above
  \item \texttt{sampler}: optional sampler function for a collection of configurations
  \item \texttt{configurations}: optional collection of configurations to use as a training set
  \item \texttt{memoize}: if true, use a memoized version of the metric
\end{itemize}
Each of those actions is semi-automated through default parameters and machine learning over a large collection of benchmarks \cite{baffier2022interpretable}.

\begin{lstlisting}[language = Julia]
function explore_learn_compose(
  domains,
  concept,
  param=nothing;
  global_iter=Threads.nthreads(),
  local_iter=100,
  metric=:hamming,
  pop_size=400,
  search=:flexible,
  complete_search_limit=1000,
  solutions_limit=100,
  sampler=nothing,
  configurations=explore(
    domains, concept, param;
    search, complete_search_limit, solutions_limit
  ),
  memoize=true,
)
  dom_size = maximum(domain_size, domains)
  solutions, non_sltns = configurations
  return learn_compose(
    solutions,
    non_sltns,
    dom_size,
    param;
    local_iter,
    global_iter,
    metric,
    pop_size,
    sampler,
    memoize,
  )
end
\end{lstlisting}

A long-term goal of \cnjl is to make the three first arguments optional too. We hope that such improvement will be used within \jc, for instance within the following more advanced examples.

\subsection{Advanced examples}
\label{subsec:advanced}

Large scale use of \cnjl is made within \jc and appears in:
\begin{itemize}
  \item \cjl: the learning script can be found in \texttt{/src/learn.jl} and can be called as \texttt{learn\_from\_icn()}.
  \item \icnbjl: an extensive collection of ICN benchmarks run on an HPC cluster. This package is not registered in the general registry of Julia packages.
\end{itemize}

@@

We envisage several directions for future improvement of ICN within \cnjl. Follows a non-comprehensive list of the most challenging features.

\paragraph*{New operations in existing layers} As the experiments have shown in \cite{richoux2020automatic,baffier2022interpretable}, some concepts are too complex to be covered with the current set of operations. The most direct solutions is to provide a broader collection of elementary operations.

\paragraph*{New layers} Applied to \efsp/\efop or not, it is likely that adding some layers of operation could cover a wider spectrum of combinatorial functions (with some cost for the interpretability and computation time).

\paragraph*{Reinforcement learning} Some limitations in the ICN parametrization and metrics could be solved at runtime with dynamic learning. In the \jc context, this could occur at the solver execution.

\paragraph*{Apply ICN to other fields and problems} Contributions and suggestions are more than welcome!

@@

The problems modelled, and the compositions extracted in this section are subject to future changes and improvements of the JuMP/JuCP packages. However, the keys ideas are presented here and examples will be updated accordingly within \jc in the future. We welcome GitHub issues and pull requests.

@@

At the moment, \cmjl hosts more than a dozen models. Along with \emph{Magic Square} introduced in Section \ref{subsec:example}, we present models for two other classical optimization problems: \emph{Golomb ruler} and \emph{minimum cut}. The choice was made to cover different type of constraints, with error functions learned from \cnjl.

Note that a model for the minimum cut problem in a network requires a matrix (graph) as input. Additionally, we add the optional argument of the interdiction of some links in the cut, which lead to an intractable problem called \emph{Network Interdiction} \cite{baffier2016parametric}.

@@

In contrast, an instance of the Golomb ruler problem does not require specific dataset. However, this problem exists as both satisfaction and optimization variants.

@@

  @constraint(m, X in AllDifferent())

  # optional for output readability
  @constraint(m, X in Ordered())

@@

Along with the magic-square model in Section \ref{sec:introduction}, the models in this zoo use the following constraints: \texttt{:all\_different}, \texttt{:dist\_different}, \texttt{:linear}, and \texttt{:ordered}\footnote{The code provided here will be updated following the results of the benchmark in \cite{baffier2022interpretable}. In particular, for \texttt{:dist\_different} and \texttt{:linear}, the current code is a hand-written function.}.\newline
